Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
make the abstract shorter

\begin{abstract}
In computational biology, the languages of choice for solving ad-hoc problems are high-level
``scripting'' languages such as Python or domain-specific statistics languages such as R,
while the language of choice for solving high-performance problems is C++.
This dichotomy creates a difficulty when computational biologists wish to experiment with a
variety of approaches to a problem, only some of which are likely to prove fruitful.
This experience report details our use of Haskell in implementing a high-performance,
computational biology application which is the first implementation of a particular
novel algorithm for protein structure and function prediction. We discuss the highlights
and difficulties of this project, as well as the potential improvements the Haskell
community might make that would ease some of these difficulties.
\end{abstract}

>>>>

\begin{abstract}
Haskell combines the flexibility and rapid prototyping of a scripting
language with performance comparable to~C++.
The Haskell language and libraries provide powerful abstractions, 
but we couldn't always get them to work!
Despite some speed bumps around profiling, debugging, and the
uncertain status of any given package, we~found Haskell's ecosystem
provided fine support for developing new algorithms in computational
biology.
\end{abstract}
